---
title: "Covid-19 Dashboard "
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(DT)
library(plotly)
library(coronavirus)
library(leaflet)
library(leafpop)
library(purrr)

confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
myData <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM") %>%   dplyr::select(Date = dateRep,Year = year ,Cases = cases, Deaths = deaths, Country = countriesAndTerritories)



CountryWiseData <- myData %>% 
                   group_by(Country) %>%
                   summarise(Confirmed_Cases = sum(Cases), Total_Deaths = sum(Deaths))%>%
                   mutate(Active_Cases = (Confirmed_Cases - Total_Deaths), 
                          Death_rate = (Total_Deaths / Confirmed_Cases)*100) 
            #%>% arrange(desc(Confirmed_Cases))
df <- coronavirus %>% 
  # dplyr::filter(date == max(date)) %>%
  dplyr::group_by(Country.Region, type) %>%
  dplyr::summarise(total = sum(cases)) %>%
  tidyr::pivot_wider(names_from =  type, 
                     values_from = total) %>%
  dplyr::mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
  dplyr::arrange(-confirmed) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(country = dplyr::if_else(Country.Region == "United Arab Emirates", "UAE", Country.Region)) %>%
  dplyr::mutate(country = dplyr::if_else(country == "Mainland China", "China", country)) %>%
  dplyr::mutate(country = dplyr::if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
  dplyr::mutate(country = trimws(country)) %>%
  dplyr::mutate(country = factor(country, levels = country))

```



Summary  
=======================================================================

Row {data-height=150}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(value = paste(myData %>%   
          dplyr::select(Cases = Cases) %>% sum()),
          caption = "Confirmed Cases",color = confirmed_color)
```

### active {.value-box}

```{r}

valueBox(value = paste(myData %>%   dplyr::select(Cases = Cases) %>% 
           sum() -  myData %>%   dplyr::select(Deaths = Deaths) %>% sum()),
           caption = "Active Cases",color = active_color)
```

 
### deaths {.value-box}

```{r}

valueBox(value = paste(myData %>%   dplyr::select(Deaths = Deaths) %>% sum()),
         caption = "Death Cases",
         color = death_color)
```



Row {data-height=400}
-----------------------------------------------------------------------
### Total cases by type(Top 50 Country) {.no-padding}

```{r}
plotly::plot_ly(data = CountryWiseData[1:50,], 
                x = ~Country, 
                y = ~Confirmed_Cases,
                type = "bar",
                name = "Confirmed cases",
                marker = list(color = confirmed_color)) %>%

    plotly::add_trace(y = ~Active_Cases,
                    name = "Active Cases",
                    marker = list(color = active_color)) %>%
  
  plotly::add_trace(y = ~Total_Deaths,
                    name = "Total Deaths",
                    marker = list(color = death_color)) %>%
  
  plotly::layout(title = "", 
                 barmode = 'stack',
                 yaxis = list(title = "Total cases(log scaled)", type = 'log'),
                 xaxis = list(title = ""),
                 hovermode = 'compare',
                 annotations = list(
                   text = paste("Last update:24 April", sep = " "),
                   xref = "paper",
                   yref = "paper",
                   showarrow = FALSE,
                  x = 0.95,
                  y = 1
                 ),
                 margin = list(
                   pad = 2
                 ))


```


Row 
-----------------------------------------------------------------------

### Death rate by countryName {.no-padding}

```{r}
plotly::plot_ly(CountryWiseData[1:50,], x = ~Country, 
                y = ~ Death_rate,
                type = 'scatter', 
                mode = 'line+markers')%>%
      layout(title = "CountryWise Death Rate", annotations=~Death_rate)


```

### CountryWise Summary {.no-padding}
```{r}

CountryWiseData[1:nrow(CountryWiseData),0:4] %>%
  DT::datatable(rownames = FALSE,escape = FALSE,
                colnames = c("Country", "Confirmed Case","Total Deaths", "Active Cases"),
                options = list(pageLength = nrow(CountryWiseData),scrollX = TRUE, scrollY=TRUE, autoWidth=TRUE, dom = 't',order = list(1, desc),
                                columnDefs = list( list(targets=c(0), visible=TRUE, width='10%')),initComplete = JS("function(settings, json) {",
                "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
                "}")))

```


Map
=======================================================================
**Map**

```{r map}
# map tab added by Art Steinmetz

cv_data_for_plot <- coronavirus %>% 
  dplyr::filter(cases > 0) %>% 
  dplyr::group_by(Country.Region,Province.State,Lat,Long,type) %>% 
  dplyr::summarise(cases = sum(cases)) %>% 
  dplyr::mutate(log_cases = 2 * log(cases)) %>% 
  dplyr::ungroup()
cv_data_for_plot.split <- cv_data_for_plot %>% split(cv_data_for_plot$type)
pal <- colorFactor(c("orange", "red","green"), domain = c("confirmed", "death","recovered"))
map_object <- leaflet() %>% addProviderTiles(providers$Stamen.Toner)
names(cv_data_for_plot.split) %>%
  purrr::walk( function(df) {
    map_object <<- map_object %>%
      addCircleMarkers(data=cv_data_for_plot.split[[df]],
                 lng=~Long, lat=~Lat,
#                 label=~as.character(cases),
                 color = ~pal(type),
                 stroke = FALSE,
                 fillOpacity = 0.8,
                 radius = ~log_cases,
                 # popup =  leafpop::popupTable(cv_data_for_plot.split[[df]],
                 popup =  popupTable(cv_data_for_plot.split[[df]],
                                              feature.id = FALSE,
                                              row.numbers = FALSE,
                                              zcol=c("type","cases","Country.Region","Province.State")),
                 group = df,
#                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })
map_object %>%
  addLayersControl(
    overlayGroups = names(cv_data_for_plot.split),
    options = layersControlOptions(collapsed = FALSE) 
  )
```


Data
=======================================================================
### Covid-19 All Country Data
```{r}
#these libraries need to be loaded
library(utils)
library(dplyr)
#read the Dataset sheet into “R”. The dataset will be called "data".

read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM") %>%   dplyr::select(Date = dateRep,Year = year ,Cases = cases, Deaths = deaths, Country = countriesAndTerritories ) %>%
   DT::datatable(rownames = TRUE, caption = 'This Data Update Automatically Every day',
            options = list(searchHighlight = TRUE, 
                           pageLength = 20,
                initComplete = JS("function(settings, json) {",
                "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
                "}")))
```


India
=======================================================================
**welcome back...**


About Me 
=======================================================================

**The Coronavirus Dashboard**

 
This Coronavirus dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. This dashboard is built with R using the Rmakrdown framework . The code behind the dashboard available [here](https://github.com/bharatbrijwasi/covid-19)



**Data**

 The input data for this dashboard is the [coronavirus](https://github.com/RamiKrispin/coronavirus) R package (dev version). The data and dashboard is refreshed on a daily bases. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv)


* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package and [leaflet](https://rstudio.github.io/leaflet/)
* Data manipulation - [dplyr](https://dplyr.tidyverse.org/), and [tidyr](https://tidyr.tidyverse.org/)
* Tables - the [DT](https://rstudio.github.io/DT/) package.



**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, [click here for fork](https://github.com/bharatbrijwasi/covid-19)


**Note:**

For any query or [feedback](https://docs.google.com/forms/d/e/1FAIpQLScIpkH7atKCNCkxaHatzK5Bw0U1KpVXZMAcSysBJ40o57ccog/viewform?fbzx=1636045108145844218&edit2=2_ABaOnud5YDSMdrUrvL0Kteg-RlkBg9xLH9RfJMzuFw7OLRLJFdUSg1LzwA), you can either open an [issue](https://github.com/bharatbrijwasi/covid-19/issues) or contact me.

**Contact person** : Bharat Sharma


**Mobile Number**  : +917244821708


**Email ID **      : bharatbrijwasi777@gmail.com


