---
title: "Covid-19 Dashboard "
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(DT)
library(plotly)
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
myData <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM") %>%   dplyr::select(Date = dateRep,Year = year ,Cases = cases, Deaths = deaths, Country = countriesAndTerritories)



CountryWiseData <- myData %>% 
                   group_by(Country) %>%
                   summarise(Confirmed_Cases = sum(Cases), Total_Deaths = sum(Deaths))%>%
                   mutate(Active_Cases = (Confirmed_Cases - Total_Deaths), 
                          Death_rate = (Total_Deaths / Confirmed_Cases)*100) 
            #%>% arrange(desc(Confirmed_Cases))

```



Summary 
=======================================================================
Row {data-height=150}
-----------------------------------------------------------------------

### confirmed cases

```{r}

valueBox(value = paste(myData %>%   
          dplyr::select(Cases = Cases) %>% sum()),
          color = confirmed_color)
```

### active cases

```{r}

valueBox(value = paste(myData %>%   dplyr::select(Cases = Cases) %>% 
           sum() -  myData %>%   dplyr::select(Deaths = Deaths) %>% sum()),
           color = active_color)
```


### Total deaths

```{r}
valueBox(value = paste(myData %>%   dplyr::select(Deaths = Deaths) %>% sum()),
         color = death_color)
```


Row {data-height=400}
-----------------------------------------------------------------------
### Total cases by type(Top 50 Country) {.no-padding}

```{r}
plotly::plot_ly(data = CountryWiseData[1:50,], 
                x = ~Country, 
                y = ~Confirmed_Cases,
                type = "bar",
                name = "Confirmed cases",
                marker = list(color = confirmed_color)) %>%
  plotly::add_trace(y = ~Active_Cases,
                    name = "Active Cases",
                    marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~Total_Deaths,
                    name = "Total Deaths",
                    marker = list(color = death_color)) %>%
  plotly::layout(title = "", 
                 barmode = 'stack',
                 yaxis = list(title = "Total cases(log scale)", type = 'log'),
                 xaxis = list(title = ""),
                 hovermode = 'compare',
                 margin = list(
                   pad = 2,
                   t=5
                 ))


```






Row 
-----------------------------------------------------------------------

### Death rate by countryName {.no-padding}

```{r}
plotly::plot_ly(CountryWiseData[1:50,], x = ~Country, 
                y = ~ Death_rate,
                type = 'scatter', 
                mode = 'line+markers')%>%
      layout(title = "CountryWise Death Rate", annotations=~Death_rate)


```

### CountryWise Summary {.no-padding}
```{r}

CountryWiseData[1:nrow(CountryWiseData),0:4] %>%
  DT::datatable(rownames = FALSE,escape = FALSE,
                colnames = c("Country", "Confirmed Case","Total Deaths", "Active Cases"),
                options = list(pageLength = nrow(CountryWiseData),scrollX = TRUE, scrollY=TRUE, autoWidth=TRUE, dom = 't',order = list(1, desc),
                                columnDefs = list( list(targets=c(0), visible=TRUE, width='10%')),initComplete = JS("function(settings, json) {",
                "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
                "}")))

```

India
=======================================================================

Map
=======================================================================


Data
=======================================================================
### Covid-19 All Country Data
```{r}
#these libraries need to be loaded
library(utils)
library(dplyr)
#read the Dataset sheet into “R”. The dataset will be called "data".

read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM") %>%   dplyr::select(Date = dateRep,Year = year ,Cases = cases, Deaths = deaths, Country = countriesAndTerritories ) %>%
   DT::datatable(rownames = TRUE, caption = 'This Data Update Automatically Every day',
            options = list(searchHighlight = TRUE, 
                           pageLength = 20,
                initComplete = JS("function(settings, json) {",
                "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
                "}")))
```

About Me 
=======================================================================

**The Coronavirus Dashboard**

Last updated: `r format(max(coronavirus::coronavirus$date), '%d %B')`

This Coronavirus dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. This dashboard is built with R using the Rmakrdown framework . The code behind the dashboard available [here](https://github.com/bharatbrijwasi/covid-19)



**Data**

 The input data for this dashboard is the [coronavirus](https://github.com/RamiKrispin/coronavirus) R package (dev version). The data and dashboard is refreshed on a daily bases. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv)


* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package and [leaflet](https://rstudio.github.io/leaflet/)
* Data manipulation - [dplyr](https://dplyr.tidyverse.org/), and [tidyr](https://tidyr.tidyverse.org/)
* Tables - the [DT](https://rstudio.github.io/DT/) package.



**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, [click here for fork](https://github.com/bharatbrijwasi/covid-19)


**Note**
For any question or feedback, you can either open an [issue](https://github.com/bharatbrijwasi/covid-19/issues) or contact me.

**Contact person** : Bharat Sharma


**Mobile Number**  : +917244821708


**Email ID **      : bharatbrijwasi777@gmail.com


